---
title: "RBassess model report"
subtitle: "Lake name"
author: "No author provided"
date: "`r Sys.Date()`"
---
<style type="text/css">
h1 { /* Header 1 */
 font-size: 24px;
}
</style>

```{r setup, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, echo = FALSE, message = FALSE,
  fig.width = 6, fig.height = 4.5,
  out.width = "650px",
  comment = "#>"
)

```

# Summary of MCMC chain {.tabset}
## Data and Model Fits

```{r fig.cap = "Figure 1. Age and length observations from the gillnet survey. Solid red line indicates mean length-at-age taken from the posterior mean."}
plot_age_length(x@.MISC$RBfit@RBdata, stan_obj = x, bubble = bubble)
```

```{r fig.cap = "Figure 2. Length observations from the gillnet survey."}
plot_length(x@.MISC$RBfit@RBdata)
```

```{r fig.cap = "Figure 3. Stocking density."}
plot_stocking_density(x@.MISC$RBfit@RBdata)
```

```{r fig.cap = "Figure 4. Length at stocking."}
plot_Lstart(x@.MISC$RBfit@RBdata)
```

```{r fig.cap = "Figure 5. Accumulated growing degree time (years) for the cohorts in the model. Dotted line is the 1-to-1 line."}
plot(x@.MISC$RBfit@RBdata@Age, x@.MISC$RBfit@RBdata@Age_adjust, xlab = "Integer Age", ylab = "Accumulated growing degree time (years)",
     typ = "o", pch = 16)
abline(a = 0, b = 1, lty = 2)
```

## Parameter Estimates

Table 1. Posterior means, standard deviation (SD), and coefficients of variation (CV).

```{r, echo = FALSE, cols.min.print = 5, rows.print = 17}
generate_summary_table(x)
```

```{r fig.cap = "Figure 6. Angler and gillnet selectivity-at-length from posterior mean."}
plot_selectivity(x@.MISC$RBfit, x)
```

## Posterior Distribution

```{r fig.cap = "Figure 7. Posterior distributions. Dotted vertical lines indicate means.", fig.height = 6, fig.width = 6}
if(is.null(y)) {
  plot_pars(RBdata = x@.MISC$RBfit@RBdata, stan_obj = x, plot.title = "", plot_type = "MCMC")
} else plot_pars(RBdata = x@.MISC$RBfit@RBdata, stan_obj = x, stan_prior = y, plot.title = "", plot_type = "MCMC_both")
```

## MCMC Diagnostics
```{r fig.height = 5, fig.width = 6, out.width = "800px", fig.cap = "Figure 8. Autocorrelation plot of MCMC chains."}
rstan::stan_ac(x)
```

```{r fig.height = 6, fig.width = 8, out.width = "800px", fig.cap = "Figure 9. Trace plot of MCMC chains."}
rstan::stan_trace(x)
```
<br /><br />
Table 2. Diagnostic statistics n_eff (effective sample size) and Rhat (Gelman-Rubin statistic) for the parameters in the model.
```{r echo = FALSE, cols.min.print = 3, rows.print = 17}
as.data.frame(summary(x)[[1]][, 9:10])
```
<br /><br />

**Note:** Additional diagnostics are available through the Shiny app in the `shinystan` package: `shinystan::launch_shinystan()`


# R version
This report was generated on: `r Sys.time()`

`r R.version.string`<br />
RBassess version `r packageVersion('RBassess')`
